Multi-view 3D Aerosol Distribution Recovery

### 2013-07-31 article.tex
bookmark

The atmosphere is discretized into a grid of $N_{\rm voxels}$ volume
elements (voxels), indexed by $k$ or $q$. In a
\emph{single-scattering} model, any SR changes direction only once on
the way to a camera. This model is valid in atmospheres that are not
very dense: inside fog and clouds this model does not apply. In this
model, radiative transfer has three steps (\cref{fig:groundgrid}):
({\tt i}) Attenuation of a SR propagating from the top of the
atmosphere (TOA) to voxel $k$. ~({\tt ii}) Light scattering at voxel
$k$, towards a camera. ~({\tt iii}) Light attenuation on the LOS from
voxel $k$ to the camera.~~ Steps~{\tt i},{\tt iii} involve the optical
depth along the light path to and from voxel $k$, as analyzed in
\cref{sec:optical-depth}.  Step~{\tt ii} involves the scattering
coefficient at voxel $k$, described in \cref{sec:scattering}.

@@

A voxel's vertical geometric thickness is $\Delta z$.  The Sun zenith
angle is $\Phi^{\rm SR}$. Denote a SR line segment between the TOA and
the center of voxel $k$ by $[{\rm SR},k]$ (See
\cref{fig:groundgrid}). This SR intersects voxel $q$. The intersection
line segment has geometric length $l_{\rm SR}(q)$, which depends on
$\Delta z$, $\Phi^{\rm SR}$ and $q$.  Define a $N_{\rm voxels}\times
N_{\rm voxels}$ matrix $\OpDistance^{\mathrm{Sun \rightarrow voxel}}$,
whose element $(k,q)$ represents $l_{\rm SR}(q)$:
\begin{equation}
  \OpDistance^{\mathrm{Sun \rightarrow voxel}}(k,q) =
  \left\{
    \begin{array}{ll}
      l_{\rm SR}(q) & \mbox{ if $q \in[{\rm SR},k]$} \\
      0  & \mbox{ otherwise}
      \label{eq:Dsv}
    \end{array}
  \right.
  \hspace{-0.05cm}
\end{equation}
The matrix $\OpDistance^{\mathrm{Sun \rightarrow voxel}}$ is sparse.
Analogously, for camera $c$, denote by $[{\rm LOS}_c,k]$ a LOS bounded
between the camera and the center of voxel $k$ (see
\cref{fig:groundgrid}).  The LOS zenith angle is $\Phi^{\rm LOS}_c$.
Suppose this LOS intersects voxel $q$. The geometric length of this
intersection line segment is $l_{\rm LOS_c}(q)$ which depends on
$\Delta z$, $\Phi^{{\rm LOS}_c}$ and $q$.  Analogously to
\cref{eq:Dsv}, we define a $N_{\rm voxels}\times N_{\rm voxels}$
sparse matrix whose element $(k,q)$ is
\begin{equation}
  \OpDistance^{\mathrm{voxel \rightarrow cam}}_c(k,q) =
  \left\{
    \begin{array}{ll}
      l_{{\rm LOS}_c}(q) & \mbox{ if $q \in[{\rm LOS}_c,k]$} \\
      0  & \mbox{ otherwise}
      \label{eq:Dvc}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}

@@

We simulated various spatial distributions, as a product of two
functions. The first function is an exponential decay~\cite{Levi1980}
with altitude $h(k)$ of voxel $k$,
\begin{align}
  w_1[h(k)] = \sfrac{1} {n^{sea level}}
  \exp\left[-\sfrac{h(k)}{H^\mathrm{aerosol}}\right],
\end{align}
where $H^\mathrm{aerosol}=2$~\si{\km}. This expresses a general trend
of reduced atmospheric density with height.

The second function, $w_2$, expresses a clustered nature of aerosol
``clouds''. We define blobs in the form of 3D ellipsoids. There may be
multiple ellipsoids suspended.  Then
\begin{equation}
  w_2(k) =
  \left\{
    \begin{array}{ll}
      1  & \mbox{ if $k\in$ any blob cluster} \\
      0  & \mbox{ otherwise}
      \label{eq:f2}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
The true aerosol distribution is then
\begin{equation}
  \label{eq:ntrue}
  {\bm n}^{\rm true}={\bm w}_1\odot {\bm w}_2  .
  \hspace{-0.05cm}
\end{equation}
As an example, we created a {\em Haze Blobs} scene using two ellipsoid
blobs (\cref{fig:results}a): the first is centered at altitude
\SI{3.3}{\km}, and has horizontal width of \SI{32}{\km} and vertical
thickness of \SI{2.8}{\km}. The second ellipsoid is centered at
altitude \SI{6.6}{\km}, and has lateral width of \SI{24}{\km} and
vertical thickness of \SI{2.1}{\km}. Note that the horizontal widths
are much larger than the vertical ones. This is consistent with scales
of atmospheric aerosol distributions.
\\

>>>>

The atmosphere is discretized into a grid of $N_{\rm voxels}$ volume
elements (voxels), indexed by $k$, $m$ or $q$. In a
\emph{single-scattering} model, any SR changes direction only once on
the way to a camera. This model is valid in atmospheres that are not
very dense: inside fog and clouds this model does not apply. In this
model, radiative transfer has three steps (\cref{fig:groundgrid}):
({\tt i}) Attenuation of a SR propagating from the top of the
atmosphere (TOA) to voxel $k$. ~({\tt ii}) Light scattering at voxel
$k$, towards a camera. ~({\tt iii}) Light attenuation on the LOS from
voxel $k$ to the camera.~~ Steps~{\tt i},{\tt iii} involve the optical
depth along the light path to and from voxel $k$, as analyzed in
\cref{sec:optical-depth}.  Step~{\tt ii} involves the scattering
coefficient at voxel $k$, described in \cref{sec:scattering}.

@@

A voxel's vertical geometric thickness is $\Delta z$.  The Sun zenith
angle is $\Phi^{\rm SR}$. Denote a SR line segment between the TOA and
the center of voxel $k$ by $[{\rm SR},k]$ (See
\cref{fig:groundgrid}). This SR intersects voxel $q$. The intersection
line segment has geometric length $l_{\rm SR}(q)$, which depends on
$\Delta z$, $\Phi^{\rm SR}$ and $q$.  Define a $N_{\rm voxels}\times
N_{\rm voxels}$ matrix $\OpDistance^{\mathrm{Sun \rightarrow voxel}}$,
whose element $(k,q)$ represents $l_{\rm SR}(q)$:
\begin{equation}
  \OpDistance^{\mathrm{Sun \rightarrow voxel}}(k,q) =
  \left\{
    \begin{array}{ll}
      l_{\rm SR}(q) & \mbox{ if $q \in[{\rm SR},k]$} \\
      0  & \mbox{ otherwise}
      \label{eq:Dsv}
    \end{array}
  \right.
  \hspace{-0.05cm}
\end{equation}
The matrix $\OpDistance^{\mathrm{Sun \rightarrow voxel}}$ is sparse.
Analogously, for camera $c$, denote by $[{\rm LOS}_c,k]$ a LOS bounded
between the camera and the center of voxel $k$ (see
\cref{fig:groundgrid}).  The LOS zenith angle is $\Phi^{\rm LOS}_c$.
Suppose this LOS intersects voxel $q$. The geometric length of this
intersection line segment is $l_{\rm LOS_c}(m)$ which depends on
$\Delta z$, $\Phi^{{\rm LOS}_c}$ and $m$.  Analogously to
\cref{eq:Dsv}, we define a $N_{\rm voxels}\times N_{\rm voxels}$
sparse matrix whose element $(k,m)$ is
\begin{equation}
  \OpDistance^{\mathrm{voxel \rightarrow cam}}_c(k,m) =
  \left\{
    \begin{array}{ll}
      l_{{\rm LOS}_c}(m) & \mbox{ if $m \in[{\rm LOS}_c,k]$} \\
      0  & \mbox{ otherwise}
      \label{eq:Dvc}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}

@@

We simulated various spatial distributions, as a product of two
functions. The first function is an exponential decay~\cite{Levi1980}
with altitude $h(k)$ of voxel $k$,
\begin{align}
  f_1[h(k)] = \sfrac{1} {n^{sea level}}
  \exp\left[-\sfrac{h(k)}{H^\mathrm{aerosol}}\right],
\end{align}
where $H^\mathrm{aerosol}=2$~\si{\km}. This expresses a general trend
of reduced atmospheric density with height.

The second function, $f_2$, expresses a clustered nature of aerosol
``clouds''. We define blobs in the form of 3D ellipsoids. There may be
multiple ellipsoids suspended.  Then
\begin{equation}
  f_2(k) =
  \left\{
    \begin{array}{ll}
      1  & \mbox{ if $k\in$ any blob cluster} \\
      0  & \mbox{ otherwise}
      \label{eq:f2}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
The true aerosol distribution is then
\begin{equation}
  \label{eq:ntrue}
  {\bm n}^{\rm true}={\bm f}_1\odot {\bm f}_2  .
  \hspace{-0.05cm}
\end{equation}
As an example, we created a {\em Haze Blobs} scene using two ellipsoid
blobs (\cref{fig:results}a): the first is centered at altitude
\SI{3.3}{\km}, and has horizontal width of \SI{32}{\km} and vertical
thickness of \SI{2.8}{\km}. The second ellipsoid is centered at
altitude \SI{6.6}{\km}, and has lateral width of \SI{24}{\km} and
vertical thickness of \SI{2.1}{\km}. Note that the horizontal widths
are much larger than the vertical ones. This is consistent with scales
of atmospheric aerosol distributions.
\\
